\documentclass[10pt,a4paper,titlepage]{article}
\usepackage[latin1]{inputenc}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}

\usepackage{fancyhdr}
\pagestyle{fancy}
\lhead{Montana State University}
\rhead{Kankelborg Research Lab}

\author{Roy Smart, Jordan Maxwell}
\title{MOSES Flight Software Operation Manual}

\begin{document}

\maketitle

\tableofcontents

\newpage

\section{Starting the MOSES Flight Computer}
\begin{enumerate}
	\item Turn on EGSE \#2
	\begin{enumerate}
		\item Log into account \textbf{(Unknown)} with password: \texttt{letmypeoplego}
		\item Run the program \texttt{MOSES\_SERVER.sh}
		\begin{enumerate}
			\item Connect the uplink com port to \texttt{/dev/ttyS5}
			\item Connect the downlink com port to \texttt{/dev/ttyS4}
			\item Confirm that the IP server port is set to port \texttt{10000}
		\end{enumerate}
		\item Run the program \texttt{MOSES\_CLIENT.sh}
		\begin{enumerate}
			\item Navigate to \texttt{File} $\rightarrow$ \texttt{Connect} and connect to the server.
		\end{enumerate}
		\item Press \texttt{CTRL + ALT + T} to open the bash shell window. This window will be referred to as Terminal \#1.
		\begin{enumerate}
			\item Enter the command \texttt{sudo minicom -s}. If needed, confirm the \texttt{sudo} command with the previous password, \texttt{letmypeoplego}.		
		\end{enumerate}
	\end{enumerate}
	\item Turn on EGSE \#1
	\begin{enumerate}
		\item Press the button to toggle the KVM switch to move keyboard control to EGSE1
		\item Log into account \texttt{Brandon}, with password \textbf{(unknown)}
		\item Start the Labview analog TM software \textbf{(Path Unknown)}
	\end{enumerate}
	\item Confirm that the Agilent \textbf{Model \# unknown} is turned on.
	\item Power up Power supply \#1 (PS1)
	\begin{enumerate}
		\item Press the button labeled \texttt{Recall} twice on the face of PS1 to recover the appropriate voltage/current settings.
	\end{enumerate}
	\item Press the button labeled \texttt{CC\_Power} on the timer/uplink deck to turn on the flight computer.
	\item Toggle the KVM switch to return to EGSE2
	\begin{enumerate}
		\item Terminal \#1 should be showing output on the screen. This is the bootup sequence of the flight computer.
		\begin{enumerate}
			\item Once the bootup sequence is complete, Terminal \#1 should be prompted with a login. Use the username \texttt{root} and the password is just one space, as in \texttt{" "}.
		\end{enumerate}
		\item Press \texttt{CTRL + ALT + T} to open another instance of bash. This window will be referred to as Terminal \#2.
		\begin{enumerate}
			\item Open an ssh tunnel by entering the command \texttt{ssh root@}\textbf{(IP address unknown).} If the system can't find the flight computer at that IP address please see the section below labeled \textbf{Locating IP adresses using NMAP}.
			\begin{enumerate}
				\item Log into the flight computer using the same passwords as before, username \texttt{root} and password one space, \texttt{" "}.
				\item Open the flight software log using the command \texttt{tail -f /moses/ramdisk/moses\_log.txt}
			\end{enumerate}
		\end{enumerate}
	\end{enumerate}
	\item The flight software is now ready to begin taking exposures.
\end{enumerate}

\section{Using the MOSES Instrument}
\subsection{Taking Exposures}
\subsection{Activating the Shutter without the ROE}
\subsection{Advanced Usage}

\section{Troubleshooting}
\subsection{Locating IP adresses using NMAP}

\end{document}